Report

### 2021-06-17 paper/appendix.Rmd
Add figures in appendices

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std",
  "piel_bm", "piel_nind")

@@

@@

loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends,
  pred_bm_rich_mono_stable_trends)

>>>>

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std",
  "piel_bm", "piel_nind")
```

# Data exploration

## Maps

```{r}
loadd(p_st_mono_trends_stable_rich_bm, st_mono_trends_stable_rich_bm)

st_cap <- paste0(
  "Repartion of the", length(st_mono_trends_stable_rich_bm), " stations used in
  the data analysis.")

@@

```{r st, fig.cap = st_cap}
p_st_mono_trends_stable_rich_bm
```

## Range of variation

```{r}
range_cap <- paste0(
  "Range of variation of variables in spatial (vertical line) and temporal
  dataset for the (A) minimum and maximum values and (B) the range (i.e. maximum
    - minimum)."
)
```

```{r range, fig.cap=range_cap, fig.height=10}
loadd(p_range)

plot_grid(plotlist = p_range, nrow = 2, labels = "AUTO")
```

## Correlation

```{r}
cor_cap <- paste0("Correlation plot among variables for spatial and temporal
  relationships. ", "Median values over temporal series in each station were
  used for spatial relationships. ", "For temporal relationships, we used the
  temporal trends in each station. Futhermore, each station was weighted by the
  average error standard on the temporal trends of the variables.")
```

```{r cor, fig.cap=cor_cap}
oldpar <- par()
loadd(corr_plot_med, corr_plot_tps)

set_names_corr <- function(mat = NULL) {
  colnames(mat) <- str_replace_all(colnames(mat), var_replacement())
  rownames(mat) <- str_replace_all(rownames(mat), var_replacement())
  return(mat)
}

corr_plot_tps %<>% set_names_corr(.)
corr_plot_med %<>% set_names_corr(.)

par(mfrow = c(1, 2))
corrplot::corrplot(corr_plot_med, type = "upper", diag = FALSE, order =
  "alphabet")
title("Spatial")
corrplot::corrplot(corr_plot_tps, type = "upper", diag = FALSE, order =
  "alphabet")
title("Temporal trends")
```

@@

loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends,
  pred_bm_rich_mono_stable_trends)
```

### 2021-06-17 report_rdv.Rmd
Add figures in appendices

loadd(data4model, rigal_classification, full_data2, summary_var_f3y)
rigal_classification$classif[[1]]

range_spatial_variable <- summary_var_f3y %>%
  select(c("station", get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  pivot_longer(!station, names_to = "variable", values_to = "values") %>%
  group_by(variable) %>% 
  summarise(min = min(values, na.rm = TRUE), max = max(values, na.rm = TRUE)) %>%
  mutate(range = max - min)

range_variable_station <- full_data2 %>% 
  select(c("station", get_biomass_var(), get_com_str_var(all = TRUE))) %>%
  pivot_longer(!station, names_to = "variable", values_to = "values") %>%
  group_by(station, variable) %>% 
  summarise(min = min(values, na.rm = TRUE), max = max(values, na.rm = TRUE))

range_variable_station %>%
  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values") %>%
  ggplot(aes(x = values, fill = minmax)) +
  geom_histogram() +
  geom_vline(data = range_spatial_variable %>%
    pivot_longer(cols = c(min, max), names_to = "minmax", values_to = "values"),
  aes(xintercept = values, color = minmax)) + facet_wrap(~variable, scale =
  "free")

# Range distibution 
range_variable_station %>%
  filter(variable %in% c(get_biomass_var(), get_com_str_var(all = FALSE))) %>%
  mutate(range = abs(max - min)) %>%
  ggplot(aes(x = range)) +
  geom_histogram() +
  geom_vline(data = range_spatial_variable, aes(xintercept = range)) +
  facet_wrap(~variable, scale = "free") 
```

>>>>

loadd(data4model, rigal_classification, full_data2, summary_var_med,
  st_mono_trends_stable_rich_bm)

loadd(p_range)

plot_grid(plotlist = p_range)
# Range distibution
```
